### 2021-07-14 src/paper/report.tex
Fix broken references.

We draw simulated samples of agents from the population structure in September 2020 and
use the model to predict recorded infection rates until the end of May 2021. See
Supplementary Materials~\ref{subsec:synthetic_population} and
\ref{sub:initial_conditions} for details. The blue line in
Figure~\ref{fig:aggregated_fit} shows that our model's predictions are very close to
officially recorded cases in the aggregate. This is also true for infections by age and
geographical region (see Supplementary Material~\ref{sec:subsec:fit_results}).

@@

Two of the most contentious NPIs concern schools and mandates to work from
home.\comment[id=K]{We should decide if we want to keep this section or prefer to show
some rapid test statistics.} In many countries, schools switched to remote instruction
during the first wave, so did Germany. After the summer break, they were operating at
full capacity with increased hygiene measures, before being closed again from
mid-December onward. Some states started opening them gradually in late February, but
operation at normal capacity did not resume until the beginning of June.
Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding
schools starting at Easter, at which point rapid tests had become widely available. We
estimate the realized scenario to have essentially the same effect as a situation with
closed schools. Under fully opened schools with mandatory tests, total infections would
have been 6\% higher; this number rises to 20\% without tests. These effect sizes are
broadly in line with empirical studies \citep[e.g.,][]{Vlachos2021}.
\comment[id=HM]{Need a back-of the envelope calculation} To use another metric, the
effective weekly reproduction number differs by $0.018$ and $0.052$, respectively. In
light of the large negative effects school closures have on children and parents
\citep{Luijten2021, Melegari2021}---and in particular on those with low socio-economic
status---these results in conjunction with hindsight bias suggest that opening schools
combined with a testing strategy would have been beneficial. In other situations, and
particular when rapid test are not available at scale, trade-offs may well be different.

>>>>

We draw simulated samples of agents from the population structure in September 2020 and
use the model to predict recorded infection rates until the end of May 2021. See
Supplementary Materials~\ref{subsec:synthetic_population} and
\ref{sub:initial_conditions} for details. The blue line in
Figure~\ref{fig:aggregated_fit} shows that our model's predictions are very close to
officially recorded cases in the aggregate. This is also true for infections by age and
geographical region (see Supplementary Material~\ref{subsec:fit_results}).

@@

Two of the most contentious NPIs concern schools and mandates to work from
home.\comment[id=K]{We should decide if we want to keep this section or prefer to show
some rapid test statistics.} In many countries, schools switched to remote instruction
during the first wave, so did Germany. After the summer break, they were operating at
full capacity with increased hygiene measures, before being closed again from
mid-December onward. Some states started opening them gradually in late February, but
operation at normal capacity did not resume until the beginning of June.
Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding
schools starting at Easter, at which point rapid tests had become widely available. We
estimate the realized scenario to have essentially the same effect as a situation with
closed schools. Under fully opened schools with mandatory tests, total infections would
have been 6\% higher; this number rises to 20\% without tests. These effect sizes are
broadly in line with empirical studies \citep[e.g.,][]{Vlachos2021}.\comment[id=HM]{Need
a back-of the envelope calculation} To use another metric, the effective weekly
reproduction number differs by $0.018$ and $0.052$, respectively. In light of the large
negative effects school closures have on children and parents \citep{Luijten2021,
Melegari2021}---and in particular on those with low socio-economic status---these results
in conjunction with hindsight bias suggest that opening schools combined with a testing
strategy would have been beneficial. In other situations, and particular when rapid test
are not available at scale, trade-offs may well be different.
